Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-02-07 paper_comparison/paper_comparison/paper_comparison.tex
major update: use effect size instead of log(effect size) to fit model
the intercept is fixed by a constant log(0.05/0.95) to give 5% power when effect size = 0

For non-linearity patterns, the power curve of RESET test climbs
aggressively from 15\% to 69\% as \(log_e(E)\) increases from 0 to 2,
while power of other tests respond inactively to the change of effect,
showing that RESET test is way more sensitive to the type of model
defects that being considered. Meanwhile, no noticeable visual features
can be spotted from the example residual plots.

@@

\caption{Comparison of power between different tests for non-linear patterns (uniform fitted values only). Main plot shows the power curves estimated using logistic regression, with dots indicating human evaluations of lineups. Surrounding lines of the visual test show the estimated power of 1000 bootstrap samples. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much non-linearity in the residuals? For the RESET test this is around log effect size 1.5, but for the visual test it is around 3.5.}\label{fig:polypower}
\end{figure}

@@

\caption{Comparison of power between different tests for heteroskedasticity patterns (uniform fitted values only). Main plot shows the power curves, with dots indicating human evaluations of lineups. Surrounding lines of the visual test show the estimated power of 1000 bootstrap samples. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much heteroskedasticity in the residuals? For the BP test this is around log effect size 1.5, but for the visual test it is around 3.}\label{fig:heterpower}
\end{figure}

@@

\caption{Comparison of power on lineups with different fitted value distributions, for conventional tests and visual tests. For visual tests, all the power curves are estimated using five evaluations on each lineup. For lineups with uniform fitted value distribution, the five evaluations are randomly sampled from the total eleven evaluations. The sampling process has been repeated for 1000 times and the corresponding power curves are drawn with transparent grey lines. The vetical dotted line is drawn to indicate where the visual pattern start to become recognisable. For both types of tests power does change. The discrete fitted value distribution substantially lowers the power of visual tests for non-linearity patterns in residual plots. For heteroskedasticity patterns, the lognormal distribution produce lower power for both types of tests.}\label{fig:different-x-dist-poly-power}
\end{figure}

@@

Throughout the three data collection periods of the human subject
experiment we conducted, residual plots rejected by visual tests are
rarely not rejected by conventional tests, but departures of residuals
that are of little practical sense to humans will often be alarmed by
conventional tests, supporting the common guidance given by experts to
utilize graphical representations of data in model diagnostics.

@@

>>>>

For non-linearity patterns, the power curve of RESET test climbs
aggressively from 7\% to 30\% as \(log_e(E)\) increases from 0 to 2,
while power of other tests respond inactively to the change of effect,
showing that RESET test is way more sensitive to the type of model
defects that being considered. Meanwhile, no noticeable visual features
can be spotted from the example residual plots.

@@

\caption{Comparison of power between different tests for non-linear patterns (uniform fitted values only). Main plot shows the power curves estimated using logistic regression, with dots indicating human evaluations of lineups. Surrounding lines of the visual test show the estimated power of 500 bootstrap samples. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much non-linearity in the residuals? For the RESET test this is around log effect size 2.5, but for the visual test it is around 3.5.}\label{fig:polypower}
\end{figure}

@@

\caption{Comparison of power between different tests for heteroskedasticity patterns (uniform fitted values only). Main plot shows the power curves, with dots indicating human evaluations of lineups. Surrounding lines of the visual test show the estimated power of 1000 bootstrap samples. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much heteroskedasticity in the residuals? For the BP test this is around log effect size 2.5, but for the visual test it is around 3.5.}\label{fig:heterpower}
\end{figure}

@@

\caption{Comparison of power on lineups with different fitted value distributions, for conventional tests and visual tests. For visual tests, all the power curves are estimated using five evaluations on each lineup. For lineups with uniform fitted value distribution, the five evaluations are randomly sampled from the total eleven evaluations. The sampling process has been repeated for 500 times and the corresponding power curves are drawn with transparent grey lines. For both types of tests power does change. The discrete fitted value distribution substantially lowers the power of visual tests for non-linearity patterns in residual plots. For heteroskedasticity patterns, normal and lognormal distributions produce lower power for both types of tests.}\label{fig:different-x-dist-poly-power}
\end{figure}

@@

According to the data collected from the human subject experiment,
residual plots rejected by visual tests are rarely not rejected by
conventional tests, but departures of residuals that are of little
practical sense to humans will often be alarmed by conventional tests,
supporting the common guidance given by experts to utilize graphical
representations of data in model diagnostics.

@@

Interestingly, the orientation of the visual pattern
